---
title: "Activity 1.2"
author: "Facundo Bautista Barbera"
format: html
output: pdf_document
editor: visual
---

## Access the cars dataset.

```{r}
#| output: false
library("tidyverse")
library(nortest)
library(moments)
```

```{r}
dataset <- cars
summary(dataset)
```

## Create tests

Test the univariate normality of speed and stopping distance. Select at least two of the methods covered in class.

### Shapiro Wilk

```{r}
shapiro_test <- shapiro.test(dataset$speed)
print(shapiro_test)

shapiro_test <- shapiro.test(dataset$dist)
print(shapiro_test)
```

### Anderson Darling

```{r}
ad_test <- ad.test(dataset$speed)
print(ad_test)

ad_test <- ad.test(dataset$dist)
print(ad_test)
```

### Kolmogorov Smirnov

```{r}
lillie_test <- lillie.test(dataset$speed)
print(lillie_test)

lillie_test <- lillie.test(dataset$dist)
print(lillie_test)
```

### Jarque Bera

```{r}
jarque_test <- jarque.test(dataset$speed)
print(jarque_test)

jarque_test <- jarque.test(dataset$dist)
print(jarque_test)
```

## QQPlot and QQLine

### Speed

```{r}
qqnorm(dataset$speed, main = "QQ Plot - Speed")
qqline(dataset$speed, col = "red")
```

### Dist

```{r}
qqnorm(dataset$dist, main = "QQ Plot - Dist")
qqline(dataset$dist, col = "red")
```

## Skweness and kurtosis

### Speed

```{r}
skewness(dataset$speed)
kurtosis(dataset$speed)
```

### Dist

```{r}
skewness(dataset$dist)
kurtosis(dataset$dist)
```

## Mean, Median, Midrange

### Speed

```{r}
mean_speed <- mean(dataset$speed)
median_speed <- median(dataset$speed)
midrange_speed <- (min(dataset$speed) + max(dataset$speed)) / 2

print(c(mean_speed, median_speed, midrange_speed))
```

### Dist

```{r}
mean_dist <- mean(dataset$dist)
median_dist <- median(dataset$dist)
midrange_dist <- (min(dataset$dist) + max(dataset
$dist)) / 2

print(c(mean_dist, median_dist, midrange_dist))
```

## Boxplot

```{r}
boxplot(dataset$speed)
boxplot(dataset$dist)
```

## Histogram

```{r}
hist(dataset$speed, probability = TRUE)
lines(density(dataset$speed), col = "red")
curve(dnorm(x, mean = mean(dataset$speed), sd = sd(dataset$speed)), from = min(dataset$speed), to = max(dataset$speed), add = TRUE, col = "blue", lwd = 2)

hist(dataset$dist, probability = TRUE)
lines(density(dataset$dist), col = "red")
curve(dnorm(x, mean = mean(dataset$dist), sd = sd(dataset$dist)), from = min(dataset$dist), to = max(dataset$dist), add = TRUE, col = "blue", lwd = 2)
```

The first plot looks like like a normal distribution, with a bit of skewness to the left. The second plot looks very skewed to the right, with a long tail on the right side.
